[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)

# TanDEM-R

R interface for downloading TanDEM-X data.
Information on the data can be found at [DLR's geoservice](https://geoservice.dlr.de/web/dataguide/tdm90/ "geoservice.dlr.de").

Basic idea is to enable such a workflow to handle TanDEM-X data:

```{r, eval = FALSE}
options("geoservice.usr" = "Max.Mustermann@mail.com")

tiffiles <- download_TanDEM()

library("stars")
vrt <- st_mosaic(tiffiles)
x <- read_stars(vrt, proxy = TRUE)
plot(x)
```

```{r, map, echo = FALSE}
library("stars")
tiffiles <- list.files("~/Data/TanDEM-X/", full.names=TRUE)
vrt <- st_mosaic(tiffiles)
x <- read_stars(vrt, proxy = TRUE)
plot(x)
```

## Installation

Via [**Devtools**](https://devtools.r-lib.org) one-liner with specifying `subdir = "pkg"`:

```
devtools::install_github("meteosimon/TanDEM-R", subdir = "pkg")
```

## Authentification at DLR geoservice

First, you have to register at [DLR](https://sso.eoc.dlr.de/tdm90/selfservice/).
Within the package I use [**keyring**](https://github.com/r-lib/keyring#readme) for handling
authentification. The default for the keyring service is `"geoservice.dlr"`.

